---
title: "p8105_hw1_sm4594"
author: "Sophia Miller"
date: "9/15/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Problem 1.

Create a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels” 

```{r problem1}

problem1_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("This", "is", "the", "first", "data", "science", "homework", "assignment"),
  vec_factor = factor(c("one", "two", "three", "one", "two", "three", "one", "two"))
)
```

Take the mean of each variable in the data frame above:
```{r means}

  mean(pull(problem1_df, norm_samp))

  mean(pull(problem1_df, norm_samp_pos))

  mean(pull(problem1_df, vec_char))

  mean(pull(problem1_df, vec_factor))
```
We are able to take the mean of the random sample as well as the logical vector, but we are unable to take the mean of the character and factor vectors.

Convert logical, character, and factor variables to numeric:

```{r convertions, results = "hide"}

  as.numeric(pull(problem1_df, norm_samp_pos)) 

  as.numeric(pull(problem1_df, vec_char))

  as.numeric(pull(problem1_df, vec_factor))

```


