---
title: "p8105_hw1_sm4594"
author: "Sophia Miller"
date: "9/15/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Problem 1.

Create a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels” 

```{r problem1_df}

problem1_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("This", "is", "the", "first", "data", "science", "homework", "assignment"),
  vec_factor = factor(c("one", "two", "three", "one", "two", "three", "one", "two"))
)
```

Take the mean of each variable in the data frame above:
```{r means}

  mean(pull(problem1_df, norm_samp))

  mean(pull(problem1_df, norm_samp_pos))

  mean(pull(problem1_df, vec_char))

  mean(pull(problem1_df, vec_factor))
```
We are able to take the mean of the random sample as well as the logical vector, but we are unable to take the mean of the character and factor vectors.

Convert logical, character, and factor variables to numeric:

```{r convertions, results = "hide"}

  as.numeric(pull(problem1_df, norm_samp_pos)) 

  as.numeric(pull(problem1_df, vec_char))

  as.numeric(pull(problem1_df, vec_factor))

```

* convert the logical vector to numeric, and multiply the random sample by the result
 
* convert the logical vector to a factor, and multiply the random sample by the result
 
* convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
Problem 2

```{r convert_multiply}

  as.numeric(
    pull(problem1_df, norm_samp_pos))*(pull(problem1_df,  norm_samp))

  as.factor(
    pull(problem1_df, norm_samp_pos))*(pull(problem1_df,  norm_samp))

  as.numeric(
    as.factor(
      pull(problem1_df, norm_samp_pos)))*(pull(problem1_df,  norm_samp))

```

#Problem 2

Create a data frame comprised of:

* x: a random sample of size 500 from a standard Normal distribution
* y: a random sample of size 500 from a standard Normal distribution
* a logical vector indicating whether x + y > 1
* a numeric vector created by coercing the above logical vector
* a factor vector created by coercing the above logical vector

```{r problem2_df}
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = x + y > 1,
  as.numeric(vec_logical),
  as.factor(vec_logical)
)
```

Make a scatterplot of y vs. x; color points using logical variable: 

```{r}
ggplot(problem2_df, aes(x = x, y = y, color = vec_logical)) + geom_point()
```





